---
title: "**Bad Plot/Good Plot**"
output: github_document
---

---
title: "Bad plot / Good plot"
output: github_document
---
# Open libraries
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(viridis)
library(phyloseq)
```

# Data set

This data set is huge. 

```{r}
summarize_genusgrp <- read.csv("summarizedtest.csv")
```


# Bad plot

This plot is horrendous. The color scheme is actually impossible to determine different communities, and what do the axes even represent? It says relative abundance, but with all of these communities listed, we can't exactly tell if this makes up the "whole community". Why are the standard deviations so off? How can they be oriented that way?

This plot breaks Tufte's (section 2) principle of presenting correct data. This data is presented in a way that can be overall confusing, and not entirely accurate. You have no knowledge of what the intention is for this plot. With all the communities split up as so, it's not informative at all. Additionally, this brings in Tufte's (section 3) idea that there should be some quantitative evidence for the plot. Here, we see that we have standard deviation bars. These bars were created arbitrarily, in sort... no NAs were removed for this, and there were multiple communities that had '0' abundance. This means that the standard deviation bars really represent almost nothing for these, and you wouldn't truly know that without asking how it was made (you may have had the suspicion, from some of the negative SD bars). This plot has a ton of information on it, however - Tufte was a fan of that! You can see the treatment groups, but.. what even do the treatment groups show? You can't gain any knowledge from this, due to the way the treatment group has been plotted.



```{r}
bp <- ggplot(data = summarize_genusgrp, aes(x = Genus, y = meanRA, fill = TRT))
bp + geom_bar(aes(color = Genus, alpha = 0.5), stat="identity", position="stack") +
  scale_y_continuous(name = "Mean Relative Abundance") +
  theme(legend.position = "bottom") +
  geom_errorbar(aes(x = Genus, ymin = meanRA-sdRA, ymax = meanRA+sdRA), width = 0.5, color = "orange", alpha = 0.9, size = 1.0) 
```

![badplot](https://github.com/Ilianora/MICR_475/blob/main/badplot_proj.pdf)

# Phyloseq

Necessary for my "good plot".

metadata <- read.csv("metadata.csv")
seqtab.nochim <- read.csv("seqtabnochim.csv")
sample_data <- read.csv("sampledata.csv")
taxa <- read.csv("taxa.csv")
ps <- merge_phyloseq(otu_table(seqtab.nochim, taxa_are_rows=FALSE), sample_data(metadata), sample_names(sample_data), tax_table(taxa))
dna <- Biostrings::DNAStringSet(taxa_names(ps))
names(dna) <- taxa_names(ps)
ps <- merge_phyloseq(ps, dna)
taxa_names(ps) <- paste0("OTU", seq(ntaxa(ps)))
ps
tax.clean <- data.frame(tax_table(ps.f))
for(i in 1:6){ tax.clean[,i] <- as.character(tax.clean[,i])}
tax.clean[is.na(tax.clean)] <- ""
for (i in 1:nrow(tax.clean)) {
  if(tax.clean[i,2] == ""){
    kingdom <- paste("Kingdom_", tax.clean[i,1], sep = "")
    tax.clean[i,2:6] <- kingdom
  } else if (tax.clean[i,3] == ""){
    phylum <- paste("Phylum_", tax.clean[i,2], sep = "")
    tax.clean[i, 3:6] <- phylum
  } else if (tax.clean[i,4] == ""){
    class <- paste("Class_", tax.clean[i,3], sep = "")
    tax.clean[i, 4:6] <- class
  } else if (tax.clean[i,5] == ""){
    order <- paste("Order_", tax.clean[i,4], sep = "")
    tax.clean[i, 5:6] <- order
  } else if (tax.clean[i,6] == ""){
    family <- paste("Family_", tax.clean[i,5], sep = "")
    tax.clean[i, 6:6] <- family
  }
}
tax_table(ps.f) <- as.matrix(tax.clean)



# Good plot

If you'd like to make a "better" standard barplot, you could do something along the lines of this. I would not argue that this is the best option, but the best option is a little over my head right now (I'd prefer some kind of geom_boxplot). We can see the top 10 genera, for each treatment. At least here, we also use colorblind friendly colors as well with the viridis package.


ps1g.10 <- merge_samples(ps.f, "TRT")
ps1g.10 <- transform_sample_counts(ps1g.10, function (x) 100* x / sum(x))
ps2g.10 <- tax_glom(ps1g.10, "Genus", NArm=TRUE)
top_genus.10 <- names(sort(taxa_sums(ps2g.10), decreasing = TRUE)[1:10])
ps3g.10 <- prune_taxa(top_genus.10, ps2g.10)
dfg.10 <- psmelt(ps3g.10)

abundplotgenus.10 <- ggplot(dfg.10, aes(Sample, Abundance, fill = Genus)) +
  geom_bar(stat="identity") +
  scale_fill_viridis(discrete = TRUE) +
  ylab("Relative Abundance (%)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 360)) +
  xlab("Dosing Frequency") +
  ggtitle("Top 10 genera") +
  theme(legend.position = "bottom") +
  guides(fill=guide_legend(nrow=5))

abundplotgenus.10

![gplot_ex](https://github.com/Ilianora/MICR_475/blob/main/gplot_ex.pdf)
