---
title: "*HW3*"
output: github_document
---

# Open libraries
Open library and data that we want to work with.

```{r Open libraries}
library(tidyverse)
install.packages("babynames",repos = "http://cran.us.r-project.org")
library(babynames)
```

# Separate data for use 
Examine the dataset, then decide what our hypothesis will be. For mine, I predict that the name Margaret's usage will decrease with time.

```{r Examine data and create new data}
glimpse(babynames)
margaret <- babynames %>%
  select(year, name, n) %>%
  filter(name %in% "Margaret")
glimpse(margaret)
```

# Plotting

Plot the dataset.

```{r Plotting}

ggplot(data = margaret, aes(x = year, y = n, color = "name")) +
  geom_line() +
  labs (title = "Popularity of Margaret", x = "Year", y = "Number of People Named Margaret") +
  theme(legend.position = "none")
```

# Results
The name Margaret peaks around the 1920s and then decreases, and the nincreases again around the 50s. The name becomes less and less frequently observed by the 2000s.
