---
title: "**Homework 5**"
output: github_document
---

# Open libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
#glimpse(diamonds)
```

# Step 1: Data frame manipulation
Print a data frame that contains the simple count of diamonds in each "cut" ("Fair", "Good", etc.)

```{r, message=FALSE, warning=FALSE}
diamonds %>%
  group_by(cut) %>%
  count()
```

# Step 2: Subset data
Randomly subset the data to 1% using dplyr functions.

```{r, message=FALSE, warning=FALSE}
subset_diamonds <- sample_frac(diamonds, 0.01)
head(subset_diamonds)
```

# Step 3: Calculation
Calculate the average size of the largest 100 diamonds in each clarity category.

```{r, message=FALSE, warning=FALSE}
diamonds %>%
  group_by(clarity) %>%
  count()
#Large diamonds
large_diamonds <- diamonds %>%
  arrange(desc(carat)) %>%
  group_by(clarity) %>%
  slice(1:100)
large_diamonds
#Calculate average size
large_diamonds %>%
  group_by(clarity) %>%
  summarise(average.size = mean(carat, na.rm = T))
```

# Step 4: Scatterplots
Scatterplot 1: a plot of the x dimension vs the y dimension
Scatterplot 2: a plot of the x dimension vs the z dimension

```{r, message=FALSE, warning=FALSE}
ggplot(diamonds) +
  geom_point(aes(x = y, y = x)) +
  labs(title = "Diamond Dimensions: X vs Y", x = "Width (y)", y = "Length (x)")
ggplot(diamonds) +
  geom_point(aes(x = z, y = x)) +
  labs(title = "Diamond Dimensions: X vs Z", x = "Depth (z)", y = "Length (x)")
#Note that there are suspicious data points
```

# Step 5: Remove suspicious data points and re-plot data

```{r, message=FALSE, warning=FALSE}
# X vs Y
diamonds_xy <- diamonds %>%
  filter(x > 3 & y < 20)
ggplot(diamonds_xy) +
  geom_point(aes(x = y, y = x)) +
  labs(title = "Diamond Dimensions: X vs Y", x = "Width (y)", y = "Length (x)")
#  X vs Z
diamond_xz <- diamonds %>%
  filter(x > 3 & z < 8 & z > 1)
ggplot(diamond_xz) +
  geom_point(aes(x = z, y = x)) +
  labs(title = "Diamond Dimensions: X vs Z", x = "Depth (z)", y = "Length (x)")
```

